---
title: "Introduction to tweetRpoll"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tweetRpoll-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, fig.height=4
)
```

## Overview

`tweetRpoll` is a R package that allows users to extract and visualize
poll data from Twitter. Our goal is to make `tweetRpoll` helpful and 
user-friendly; any R beginner can effectively gain access to the data 
and make their own data-driven decisions.

To use this package, follow the installation guide on README and 
install this package.  Then, import the package.

```{r setup}
library(tweetRpoll)
```

## Functions
    
### Extract tweet IDs with `get_polls_from_user`:       
`get_polls_from_user` extracts tweet IDs of tweets that contain polls 
for a Twitter user given their handle (i.e. PollzOnTwitta). This function 
requires Twitter API credentials. Users need to store their credentials 
in a `.Renviron` file in the root directory. 

```{r}
get_polls_from_user('PollzOnTwitta')
```

### Extract poll data with `get_poll_by_id`:       
`get_poll_by_id` extracts poll information such as poll questions, 
poll options, and poll responses, from Twitter given the tweet ID 
returned from the `get_polls_from_user` function.

```{r}
get_poll_by_id(1239677495487737856)
```
### Visualize poll data with `visualize_poll`:       
`visualize_poll` takes in the output of the `get_poll_by_id` 
function and visualizes the poll information. The function provides
option to include additional information in the text box if at least 
one of the arguments (1) show_user, (2) show_duration, and (3) show_date 
is set to True.

```{r}
poll_info <- get_poll_by_id(1239677495487737856)
visualize_poll(poll_info)
```
